---
title: "Assignment 5 - Analysis"
output: html_notebook
---

* Nadejda Boev (20056079)
* Due Date - 2022/02/16
* Github user - 16nbb1
* Github link - https://github.com/16nbb1/Biol432_A5_Rentrez

```{r out.width="300px"}
url <- "https://upload.wikimedia.org/wikipedia/commons/f/f3/Borrelia_burgdorferi_%28CDC-PHIL_-6631%29_lores.jpg"
knitr::include_graphics(url)
```

Learn more 
[about Borrelia burgdorferi from Wikipedia](https://en.wikipedia.org/wiki/Borrelia_burgdorferi)


## Loading in packages and Sequences csv

```{r}
library(dplyr)
(df  = read.csv("./Sequences.csv"))
```

## Counting A/T/C/G

Count the number of each base pair (A, T, C and G), in each of the three sequences

- I've looped through all my rows and done a strsplit and searched annd tabulated each individual letter from all the sequences in each row i
- This gets appended to the larger dataframe
- I've then printed out the sequence and printed out the full row using the row index

```{r}

for (i in 1:nrow(df)) {
  
  df[i,'A'] = (data.frame(rbind(table(strsplit(df$Sequence[i], ""))))$A)
  df[i,'T'] = (data.frame(rbind(table(strsplit(df$Sequence[i], ""))))$T)
  df[i,'C'] = (data.frame(rbind(table(strsplit(df$Sequence[i], ""))))$C)
  df[i,'G'] = (data.frame(rbind(table(strsplit(df$Sequence[i], ""))))$G)
  
  # PRINTING  OUT
  print(df$Sequence[i])
  print(df[i,])

}

```


## Calculate GC Content (% of nucleotides that are G or C) and create a final table showing GC content

- Since I have the A/T/C/G totals from above, I can use dplyr's mutate to calculate the number of G/Cs across the whole sequence
  - I've presented it as a percentage
- I then renamed and shuffled the column names to match the exapple

```{r}
(gc = df %>% 
  mutate(GC = sprintf("%0.1f%%", GC_Content = 100*(C+G)/ (A+T+C+G)),
         ID = gsub(">", "", unlist(lapply(strsplit(df$Name, " "), '[[', 1)))) %>% 
  select(ID, GC) %>% 
  rename('Sequence ID'= ID, 'GC Content'= GC))
```






